Draft

### 2017-08-31 Thesis/Draft.Rmd
Add D-Tracking Rule

---
title: "Draft"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \usepackage{hyperref}
   - \usepackage[lined,boxed]{algorithm2e}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{definition}{Definition}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   - \newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 2
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

@@

# Thresholding Bandit Problem \label{chap:ThresholdingBanditProblem}

@@

\begin{theorem}[Theorem 2, Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathcal{B}$. Assume that all arms $\nu_i$ of the problem are R-sub-Gaussian with means $\mu_i$. Let $\tau \in \mathbb{R}, \epsilon \geq 0$. Algorithm APT's expected loss is upper bounded on this problem as 
\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
(-\frac{1}{64R^2}\frac{T}{H} + 2 \log (T) + 1)K)) \end{equation*}

@@

\begin{align*}
\mathbb{P}(\tilde{\xi}) & = & 1-\mathbb{P}(\xi^C) \\
& = & 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
& \geq & 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
& \geq & 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
\end{align*}

@@

\begin{align*}
|\hat{\mu}_i(t) - \mu_i| & = & |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
& \geq & || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
& \geq & |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
& \geq & |\hat{\Delta}_i(t) - \Delta_i|
\end{align*}

@@

\begin{align*}
B_k(t) & \geq & \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
& \geq & \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
\end{align*}

@@

## Lower Bound: Theorem and Proof \label{sec:LowerBoundLocatelli}

@@

*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem \ref{theorem:Locatelli2016Theorem1} of Locatelli et al. (2016), a lower bound for the thresholding bandit problem is shown. The basic idea is as follows. The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions. To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario. Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).

To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g. If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$. Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$. Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$. It is easy to see that in this case, this is equivalent to a "flip around the threshold". Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.

The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms. Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$. This is a product distribution where the $K$ different means all lie above the threshold. We would hope that an algorithm classifies the means accordingly. However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$). We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.

For each of the $K$ arms, we introduce an alternative model of the following kind. Before the start of the algorithm, we introduce a slight variation in the setup. The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem. However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$. Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above. Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$. This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.

As in Locatelli et al. (2016), we let for $i \leq K$, $\mathbb{P}_{\mathcal{B}^i}$ define the probability distribution describing all samples that a bandit strategy can potentially collect up to horizon $T$, i.e. according to the samples $(X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}$. $(T_k)_{k\leq K}$ denotes the number of samples collected on arm $k$ until time $T$.

### Reminder about the goal of the proof

At this point, we have defined a finite set of problems of Gaussian distributions with fixed variance 1 for a given set of set of gaps between the means of the distributions and the threshold, $(d_k)_k$. We will now proof a lower bound on the worst case regret of any algorithm; that is, the maximum error probability that even the best algorithm makes on this problem.

Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means. In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$. Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$. Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.

In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$. Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$. The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$. However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models. We can write this now as

In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$. This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state. In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor. This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$. By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.

We will define the change of distribution in terms of the empirical log-likelihood for our case. Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence. So let us first introduce the empirical Kullback-Leibler divergence.

Let every $\nu_i, \nu_i'$ be dominated by the Lebesgue measure $\lambda$. Then their density functions are given by $f_i = \frac{\der \nu_i}{\der \lambda}$ and $f_i' = \frac{\der \nu_i'}{\der \lambda}$ respectively. For $T \geq t \geq 0$, define the empirical Kullback-Leibler divergence as

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
\end{align*}

Since we consider Gaussian distributions with variance 1, we have density functions $f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)$ and $f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)$. Plugging this into the above definition of the empirical Kullback-Leibler divergence, we easily see

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
\end{align*}

We are now ready to state the change of distribution. As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$. When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took. The change of distribution is then defined as:

For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.

It is easy to see that

Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that. In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$. Thus we can write:

where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.

What is left to show before we have our final bound is a bound on $T_i$. To show that any algorithm has a certain bound on its error, it only makes sense that every arm has to pulled at least a certain amount of times. Consequently, no arm should be pulled exclusively.

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
\end{align*}

Furthermore, we know that the sum of the individual arm pulls has to be equal to the overall number of pulls (equal to the budget in the fixed budget sense), $\sum_i T_i = T$, and furthermore we know that $T_i>0$. The latter holds since any reasonable algorithm has to check each arm at least once in our setup. This is because we need to check each arm's performance in comparison to the threshold. Thus it is easy to show that $\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}$. To see this, assume the opposite: $\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}$. This implies however $\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T$ which is a contradiction.

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
\end{align*}

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
\end{align*}

Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss over all $\mathcal{B}_i$. By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug in our previous calculations:

\begin{align}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
\end{align}

@@

In what follows, we first examine in \autoref{chap:KullbackLeiblerPureExploration} how information theoretic quantities are employed in the best arm identification and Top-$m$ problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al. (2016). Before introducing a new algorithm for the thresholding bandit problem based on Kullback-Leibler divergences in \autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the variance-based approaches in \autoref{chap:VarianceBasedAlgorithms}.

@@

# Kullback-Leibler Complexity of Pure Exploration \label{chap:KullbackLeiblerPureExploration}

In the previous chapter, we discussed the thresholding bandit problem as presented in Locatelli et al. (2016). Doing so, we came across the complexity term $H = \sum_{i=1}^{K} \Delta_i^{-2}$. Furthermore, we noted the fact that an algorithm and bounds based on *only* the gap between the respective mean and the threshold are useful in the case of sub-Gaussian problems. Furthermore, even for the case of Bernoulli arms, which are sub-Gaussian since their feedback is bounded on $[0,1]$, the gap $\Delta$ becomes less and less appropriate in situations in which both $\mu$ of the Bernoulli, and $\tau$ are very close to 0 or 1.

Even though the complexity $H$ enjoys popularity in the literature of the best $m$ arm identification problem, $m \geq 1$, Kaufmann et al. (2016) show explicitly that $H$ is mainly useful for problems of Gaussian distributions. Indeed, they go so far as to define new measures of complexity that are based on information theoretic measures. Using these, they then frame $H$ as an approximation to their measures in the case of Gaussian distributions. This underlines the fact that Bernoulli distributions with small means have to be treated differently than Gaussian distributions.

For the current chapter, we adopt the notation of Kaufmann et al. (2016) to ease a comparison with their arguments.

## Complexity of Best-Arm and Top-*m* Identification

Instead of the thresholding bandit problem, we now consider the problem of identifying the best $m$ out of $K$ arms, that is, the Top-$m$ problem. While we previously looked at a fixed budget formulation, we now mainly focus on a fixed confidence problem: We hold the confidence $1-\delta$ fixed at which a strategy returns the correct $m$ arms while trying to reach this confidence in a way that minimizes the sample complexity $\mathbb{E}_{\nu}[\tau]$, that is, the expected number of overall draws of the arms. $\tau$ is also called the stopping time of the algorithm. The goal of algorithms is to identify $\mathcal{S}_m^*$, the set of the $m$ arms with the largest means. If we let $(\mu_1, \dots, \mu_K)$ be the vector of the means of the arms, then let $(\mu_{[1]}, \dots, \mu_{[K]})$ be the tuple in which the means are arranged in decreasing order. For the rest of this chapter, we consider only settings with arms for which $\mu_{[m]} > \mu_{[m+1]}$; we demand the set of the top $m$ arms, $\mathcal{S}_m^*$, to be unique. After the sampling phase, we require any algorithm to return the set $\hat{S}_m \subset \{1,\dots,K\}$ of $m$ arms that the algorithm believes to have the largest means. In the case of fixed confidence, we fix $\delta$ at the beginning, such that the algorithm only stops sampling when $\mathbb{P}_{\nu}(\hat{S}_m = \mathcal{S}_m^*) \geq 1-\delta$. We try to find algorithms who fulfill this condition as quickly as possible. Algorithms which minimize the expected stopping time (or number of draws), $\mathbb{E}_{\nu}[\tau]$.

To arrive at the new measure of complexity proposed by Kaufmann et al. (2016), it will actually make sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ in the case of fixed confidence problems. This bound is given in their Theorem 4 (for common confidence levels of $\delta \leq 0.15$).

@@

Given that we are again in the Top-$m$ setting, the proof idea is similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in that we again consider problems where we switch arms around the limit seperating the two groups of arms as given implicitly by $\mu_{[m]}$ and $\mu_{[m+1]}$. The hope here being that these methods could be applied to the thresholding bandit problem where the threshold of course gives the limit between the arms above and below the threshold. As we have seen in chapter 1, this flip around the threshold was of course used in the proof of the lower bound in Theorem 1 of Locatelli et al. (2016). However, there, again, the distributions were assumed to be Gaussian. This brings the big advantage that the Kullback-Leibler divergence becomes symmetric, and the feedback can take values on all $\mathbb{R}$. And by using the complexity measure $H(\nu)$, it is also clear that there exists an arm that is undersampled with respect to its contribution to the overall complexity of the problem (or sampled exactly according to its contribution), which leads to leads to a convenient upper bound on this arms number of draws which is again employed in both the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al. (2016). It is not clear yet, whether the same can also be done with other complexity measures.

@@

Given a lower bound adapted to the new complexity $H^{\text{EVT}_{pf}}$, the Zhong et al. (2017) show that the EVT$_pf$ algorithm is optimal in that its upper bound matches the lower bound. Furthermore, they compare their algorithm in experiments against the APT algorithm. The experiments use data generated from uniform distributions. Each experiment compares 100 arms with variances picked at random from a range of possible variances. Over three experiments, the range of variances is varied from small to large, where the authors expect their algorithm to show the largest advantage compared to APT on the problem with small variances. Interestingly, they report the largest advantage of their variance based algorithms in comparison to APT when the variances are very small; given they only consider problems bounded on a support of $[0,1]$, $\sigma_i \ll 1$. In this case the problem complexity $H^{\text{EVT}_{pf}}$ can be much smaller than $H^{APT}$ -- the EVT algorithm profits more from distributions that are simple to estimate in terms of their variance than the APT algorithm does.

@@

### Likelihood Ratio for Univariate Exponential Family of Distributions

@@

>>>>

---
title: "Draft"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \usepackage{hyperref}
   - \usepackage[lined,boxed]{algorithm2e}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{definition}{Definition}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   - \newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 2
    #latex_engine: xelatex
fontsize: 11pt
urlcolor: blue
---

@@

# The Thresholding Bandit Problem \label{chap:ThresholdingBanditProblem}

@@

\begin{theorem}[Theorem 2, Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathcal{B}$. Assume that all arms $\nu_i$ of the problem are R-sub-Gaussian with means $\mu_i$. Let $\tau \in \mathbb{R}, \epsilon \geq 0$. Algorithm APT's expected loss is upper bounded on this problem as 
\begin{equation*} \mathbb{E}(\mathcal{L}(T)) \leq \exp
\Big(-\frac{1}{64R^2}\frac{T}{H} + 2 \log((\log(T) + 1)K)\Big) \end{equation*}

@@

\begin{align*}
\mathbb{P}(\tilde{\xi}) & = 1-\mathbb{P}(\xi^C) \\
& = 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
& \geq 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
& \geq 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
\end{align*}

@@

\begin{align*}
|\hat{\mu}_i(t) - \mu_i| & = |(\hat{\mu}_i(t) - \tau) - (\mu_i - \tau)| \\
& \geq || \hat{\mu}_i(t) - \tau | - |\mu_i - \tau|| \\
& \geq |(|\hat{\mu}_i(t) - \tau| + \epsilon) - (|\mu_i - \tau| + \epsilon)| \\
& \geq |\hat{\Delta}_i(t) - \Delta_i|
\end{align*}

@@

\begin{align*}
B_k(t) & \geq \Big(\Delta_k - \sqrt{\frac{T\delta^2}{HT_k(t)}}\Big) \sqrt{T_k(t)} \\
& \geq \Big(\Delta_k - \sqrt{\frac{2}{h_k}}\delta \Big)
\end{align*}

@@

## Lower Bound for the Thresholding Bandit Problem \label{sec:LowerBoundLocatelli}

Locatelli et al. (2016) also provide a general lower bound on the probability of error in the thresholding bandit problem. The bound is derived for a specified set of problems through a change in distribution as common in the multi-armed bandit literature (compare for example Audibert et al., 2010, or Kaufmann et al., 2016). For any of these problems, the largest probability of error that the best algorithm incurs is still lower bounded by the bound given below.

@@

A proof of the lower bound is given in the Appendix in \autoref{sec:AppendixAPTLB}.

If we write the lower bound as $LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)$ and the upper bound as
$UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)$, we see that $LB$ and $UB$ match up to multiplicative constants and the $(\log(T)+1)K$ term which is negligiable in comparison with the exponent for large $T$ as shown in Locatelli et al. (2016), which makes the APT algorithm order optimal.

@@

In what follows, we first examine in \autoref{chap:KullbackLeiblerPureExploration} how information theoretic quantities are employed in the best arm identification and Top-$m$ problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al. (2016). Before introducing a new algorithm for the thresholding bandit problem based on Kullback-Leibler divergences in \autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.

@@

# Information Theoretic Complexity of Pure Exploration Bandits \label{chap:KullbackLeiblerPureExploration}

The previous chapter introduces the thresholding bandit problem as described in Locatelli et al. (2016), and with the APT strategy a first algorithm that is simple, yet order-optimal for large budgets. However, we end with the conclusion that a distance measure between the distributions and the threshold based on the Kullback-Leibler divergence might be more useful than the simple gap $\Delta^2_i = (\mu_i - \tau_i)^2$ employed so far. Indeed, citing Kaufmann et al. (2016), we note that the complexity $H$ used so far can be considered a sub-Gaussian approximation of a better complexity measure based on information theoretic measures like the Kullback-Leibler divergence.

In order to give more intuition to why that is the case, and in what ways information theoretic measures can be introduced to measure the complexity of bandit problems, we now turn to Kaufmann et al. (2016) and Garivier and Kaufmann (2016). The latter describes a strategy based on Kullback-Leibler divergences for the best-arm identification problem, while the first derives complexity measures based on the divergence. Ideally, their work offers methods that can inform our work of extending the thresholding bandit problem. In what follows, we adopt the notation of Kaufmann et al. (2016) to ease a comparison with their arguments.

## Complexity Measures for Best-Arm and Top-*m* Identification \label{sec:KaufmannEtAl2016}

Instead of the thresholding bandit problem, Kaufmann et al. (2016) consider the problem of identifying the best $m$ out of $K$ arms, that is, the Top-$m$ problem. They describe their a bandit model $\nu$ also by $K$ arms characterized by probability distributions $\nu_a$, $a \in \{1,...,K\}$ with mean $\mu_a$. As before, a learner decides at any time step $t=1,2,...,$ an arm $A_t \in \{1,...,K\}$ for which he observes the independent reward $Z_{t} \sim \nu_{A_t}$. The learner aims to find the $m$ out of $K$ arms with the largest expected reward. This set of arm indices is denoted by $\mathcal{S}_m^*$. Kaufmann et al. write the in decreasing order sorted means $(\mu_{1}, ..., \mu_{K})$ as the K-tuple $(\mu_{[1]}, ..., \mu_{[K]})$. Based on this, they require that $\mu_{[m]} > \mu_{[m+1]}$ such that the solution $\mathcal{S}_m^*$ is unique. The class of bandit problems $\nu$ for which the latter condition holds is called $\mathcal{M}_m$ by Kaufmann et al. At the end of the sampling procedure, after $T$ samples (denoted by $\tau$ in Kaufmann et al.) the learner is required to return a classification $\hat{\mathcal{S}}_m$. This classification is then evaluated by the loss function $\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)$. This binary loss is of course very similar to the loss in the thresholding bandit problem. We can now define a strategy of the learner as $\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)$: The strategy defines how he chooses an arm, how many samples are observed, and how the arms are classified in the end.

When introducing the thresholding bandit setting, we did not mention the fact that the budget $T$ does not need to be fixed upfront. Indeed, the setting in which the budget is *not* fixed upfront might be more popular among the best arm identification and top-$m$ literature. This setting is called *fixed-confidence*, while the setting we considered so far is called *fixed-budget*. In the fixed-budget setting, we run algorithms for $T$ samples and then compare them based on their expected loss, $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)$ as we have seen in $\autoref{sec:Setup}$. Alternatively, consider a $\delta$-PAC strategy $\mathcal{A}(\delta)$for which holds for every problem $\nu \in \mathcal{M}_m$ that the classification holds at least with confidence level $1-\delta$, that is, $\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta$. The strategy has to achieve this level of confidence in its prediction before it is allowed to stop sampling. This is the fixed-confidence case, in which the budget $T$ is no longer fixed upfront, but becomes a random variable. We compare algorithms by their expected number of draws $\mathbb{E}_{\nu}[T_{\delta}]$ and prefer those which arrive at the confidence level $1-\delta$ with a smaller expected budget.

Following Kaufmann et al. (2016), in the fixed confidence setting, a family of strategies $A = (\mathcal{A}(\delta))_{\delta \in (0,1)}$ is called PAC if for every $\delta$, $\mathcal{A}(\delta)$ is $\delta$-PAC. On the other hand, in the fixed budget setting, a family of strategies $A = (\mathcal{A}(t))_{t \in \mathbb{N}}$ is called consistent if $p_t(\nu) \rightarrow 0$ as $t \rightarrow \infty$ for every problem $\nu \in \mathcal{M}_m$.

Given this setup, we can now follow the arguments of Kaufmann et al. (2016) to deduce complexity measures for the top-$m$ problem. As alluded to earlier, these complexity measures will rely on the Kullback-Leibler divergence in contrast to the complexity $H$ used by Locatelli et al. (2016). Also, when discussing $H$, we so far described it as complexity as it measures the difficulty of the problem by measuring the distance between arms and the threshold. Kaufmann et al. approach complexity instead from how many samples (what error probability) one can expect to need in the fixed confidence (fixed budget) setting. Thus, in order to arrive at their new measure of complexity, it makes sense to first follow their arguments to a general lower bound on the sample complexity $\mathbb{E}_{\nu}[\tau]$ in the case of fixed confidence top-$m$ problems. This bound is given in their Theorem 4 (for common confidence levels of $\delta \leq 0.15$).

@@

Given that we are again in the Top-$m$ setting, the proof idea is similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in that we again consider problems where we switch arms around the limit seperating the two groups of arms as given implicitly by $\mu_{[m]}$ and $\mu_{[m+1]}$. The hope here being that these methods could be applied to the thresholding bandit problem where the threshold of course gives the limit between the arms above and below the threshold. As we have seen in chapter 1, this flip around the threshold was of course used in the proof of the lower bound in Theorem 1 of Locatelli et al. (2016). However, there, again, the distributions were assumed to be Gaussian. This brings the big advantage that the Kullback-Leibler divergence becomes symmetric, and the feedback can take values on all $\mathbb{R}$. And by using the complexity measure $H(\nu)$, it is also clear that there exists an arm that is undersampled with respect to its contribution to the overall complexity of the problem (or sampled exactly according to its contribution), which leads to a convenient upper bound on this arms number of draws which is again employed in both the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in Locatelli et al. (2016). It is not clear yet, whether the same can also be done with other complexity measures.

@@

Given a lower bound adapted to the new complexity $H^{\text{EVT}_{pf}}$, the Zhong et al. (2017) show that the EVT$_{pf}$ algorithm is optimal in that its upper bound matches the lower bound. Furthermore, they compare their algorithm in experiments against the APT algorithm. The experiments use data generated from uniform distributions. Each experiment compares 100 arms with variances picked at random from a range of possible variances. Over three experiments, the range of variances is varied from small to large, where the authors expect their algorithm to show the largest advantage compared to APT on the problem with small variances. Interestingly, they report the largest advantage of their variance based algorithms in comparison to APT when the variances are very small; given they only consider problems bounded on a support of $[0,1]$, $\sigma_i \ll 1$. In this case the problem complexity $H^{\text{EVT}_{pf}}$ can be much smaller than $H^{APT}$ -- the EVT$_{pf}$ algorithm profits more from distributions that are simple to estimate in terms of their variance than the APT algorithm does.

@@

### Likelihood Ratio for Univariate Exponential Family of Distributions \label{sec:LRforUnivariateExponentialFamily}

@@

We now compare the algorithms introduced in the previous chapters in simulations and experiments against each other to evaluate their performance. We first perform experiments on synthetic data in \autoref{sec:SyntheticData}. We then use Bernoulli time series data collected by the online shop Amorelie to evaluate the algorithms on real world data in \autoref{sec:RealData}.
